Fission product decay chain equilibria in \zirconia

### 2019-01-25 manuscript.tex
Add fission yield curve

Nuclear fuel claddings have unique materials challenges associated with them owing to the highly active environment and creation of unstable isotopes. Corrosive species in the pin such as iodine can be produced directly as a result of fission of uranium fuel. While it is known that iodine plays a role in SCC, one must also consider that these iodine nuclei are unstable. Fission of uranium will produce iodine precursors, mainly unstable isotopes of tellurium. Both iodine and tellurium are relatively common fission products, with combined independent yields from thermal fission of U$_{235}$ above 5\% \cite{kennett1956mass, iodine129fissionyield, imanishi1976independent, iaeafissionyield, iodine132, amiel1975odd}. \\

@@

@@

        \addplot[no marks, dashed, draw=black] table [x=pO2, y=XesubO{3},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{O}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};

@@

         \addplot[no marks, dashed, draw=red] table [x=pO2, y=XesubZr{-5},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{Zr}^{'''''}}};

@@

        \addplot[no marks, dashed, draw=black] table [x=pO2, y=XesubO{3},]{dat/xe_tet_10-3.dat}; 

@@

        \addplot[no marks, dashed, draw=red] table [x=pO2, y=XesubZr{-5},]{dat/xe_tet_10-3.dat}; 

>>>>

Nuclear fuel claddings have unique materials challenges associated with them owing to the highly active environment and creation of unstable isotopes. Corrosive species in the pin such as iodine can be produced directly as a result of fission of uranium fuel. While it is known that iodine plays a role in SCC, one must also consider that these iodine nuclei are unstable. Fission of uranium will produce iodine precursors, mainly unstable isotopes of tellurium. Both iodine and tellurium are relatively common fission products, with combined independent yields from thermal fission of U$_{235}$ above 5\% \cite{kennett1956mass, iodine129fissionyield, imanishi1976independent, iaeafissionyield, iodine132, amiel1975odd}. In addition, xenon and caesium are also common fission products, as shown in Figure \ref{fig:fissionyield}, with fission product masses firmly within the heavy section of the bi-modal fission product distribution curve.    \\

@@

\begin{figure}
    \centering
    \includegraphics[height=11cm]{img/fissionyield.png}
    \caption{Plot of the percentage yield of nuclei with a given mass following a fission event. Range of masses corresponding to isotopes of Te, I, Xe and Cs are highlighted.}
    \label{fig:fissionyield}
\end{figure}

@@

        %\addplot[no marks, dashed, draw=black] table [x=pO2, y=XesubO{3},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{O}^{\textperiodcentered\textperiodcentered\textperiodcentered}}};

@@

         %\addplot[no marks, dashed, draw=red] table [x=pO2, y=XesubZr{-5},]{dat/xe_tet_10-5.dat}; \addlegendentry{\ch{Xe_{Zr}^{'''''}}};

@@

        %\addplot[no marks, dashed, draw=black] table [x=pO2, y=XesubO{3},]{dat/xe_tet_10-3.dat}; 

@@

        %\addplot[no marks, dashed, draw=red] table [x=pO2, y=XesubZr{-5},]{dat/xe_tet_10-3.dat}; 
